---
title: "package(Rdeepsledge) "
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Rdeepsledge}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r Dépendances, include=FALSE}
#' @importFrom Rdeepsledge DeepS_location DeepS_find_laser DeepS_correct_laser DeepS_darkzone DeepS_gridpic45 rDeepS_PictoBIIGLE
#' Dependencies of the package
#' @useDynLib Rdeepsledge

```

```{r setup, include=FALSE}
library(Rdeepsledge)

knitr::opts_chunk$set(echo = TRUE, fig.align="center",warning = FALSE,message = FALSE,error = TRUE)
file_path <- system.file("extdata", "MPO_REFUGE_source.RData", package = "Rdeepsledge")
library(ggplot2)
library(kableExtra)
library(knitr)
load(file_path)
loclasers <- dat

```



# Introduction

The `Rdeepsledge` package is a toolbox designed for underwater surveys using a benthic sledge and image processing. The package includes functions for various tasks:

- **`DeepS_location()`**: Estimates the sledge location (longitude and latitude) from the boat position.
- **`DeepS_find_laser()`**: Extracts twin green laser positions from a video.
- **`DeepS_correct_laser()`**: Corrects laser positions.
- **`DeepS_gridpic45()`**: Adds a grid with 45 knots to images for sediment proportion estimation.
- **`DeepS_darkzone()`**: Estimates dark zones in images to improve the accuracy of surface observations.
- **`DeepS_PictoBIIGLE()`**: Imports lists of numerous pictures for BIIGLE.


# Installation

To install *RDeepSledge* Package, use **devtools::install_github("FROBIN02/Rdeepsledge")**.

## Estimating Sledge Location from Boat Position


*in process*


## Extraction of laser point locations with **DeepS_find_laser()**

Note: the AV package must be installed separately.


```{r find laser,  eval = FALSE, echo = TRUE}

library(Rdeepsledge)

MP4_file <- file.choose ()

loclasers<- DeepS_find_laser(MP4_file,FALSE,120)

```

Here, *MP4_file* is your video file, *FALSE* is the parallelization option (not stable for this version), and the number *120* corresponds to the number of frames between each estimation.

**WARNING** This function may run for several hours,days. The conversion of the video into frames can take up space, but the temporary folder is deleted at the end of the execution.


## Example for Correcting Laser Position Files with  **DeepS_correct_laser()**

```{r exemple laser, eval=FALSE,message=FALSE}

library(Rdeepsledge)

loclasers <- read.table("laser_position#yourvideo#.txt") # in "USER/document"

```


The file extracted from the video is saved as `"RESULT"`. Additionally, a backup of this file is stored in the `USER/Documents` directory with the name `laser_position_yourvideo.txt`.

For demonstration purposes, the data file `MPO_REFUGE_source.RData` is used in place of the actual video data file.


```{r corr laser data,eval=TRUE,warning=FALSE,message=FALSE}
library(Rdeepsledge)

mylaser_coor <- DeepS_correct_laser(loclasers)

```

exemple de données form **MPO IML Pêches et Océans Canada**


```{r cor res, echo=FALSE,eval=TRUE,message=FALSE,results='asis'}
library(knitr)
tabsyn <- head(mylaser_coor$DATA)
   tabsyn %>%
  kbl(caption = "Table 1:tableau de données avec balise") %>%
  kable_classic(full_width = T, html_font = "Cambria")
```

*The details of the fields are not yet available for this version...*

Next, a figure extracted from the corrected data. 

```{r corr laser graph,echo=FALSE, warning=FALSE, message=FALSE,fig.width=8, fig.height=8, results='asis'}

mylaser_coor$GRAPH

```

## Creating grid on picture with **DeepS_gridpic45()**


Before importing to annotation software like BIIGLE, **DeepS_gridpic45()** helps by creating a grid with 45 knots on each image. This grid can assist in estimating sediment proportions. All images are saved in the **GRID** directory. 


```{r DeepS_gridpic45,eval=TRUE,warning=FALSE,message=FALSE}

library(Rdeepsledge)

mydir <- "path/to/your/image/directory"

DeepS_gridpic45(mydir)

```

## Estimating Dark Zones on Images with **DeepS_darkzone()**


*in process*


## Creating a Picture List for BIIGLE Import with **DeepS_PictoBIIGLE()**


This function helps create a list of picture names in a **.txt** file from a directory of pictures.

```{r rDeepS_PictoBIIGLE,eval=TRUE,warning=FALSE,message=FALSE}
library(Rdeepsledge)

 mydir <- "path/to/your/image/directory"
 
 DeepS_PictoBIIGLE(mydir)

```


