---
title: "Rdeepsledge"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Rdeepsledge}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r Dépendances, include=FALSE}
#' @importFrom Rdeepsledge DeepS_location DeepS_find_laser DeepS_correct_laser
#' Dépendances du package
#' @useDynLib Rdeepsledge

```

```{r setup, include=FALSE}
library(Rdeepsledge)

knitr::opts_chunk$set(echo = TRUE, fig.align="center",warning = FALSE,message = FALSE,error = TRUE)
file_path <- system.file("extdata", "MPO_REFUGE_source.RData", package = "Rdeepsledge")
library(ggplot2)
library(kableExtra)
library(knitr)
load(file_path)
loclasers <- dat

```



# Introduction

The RDeepSledge package is a toolbox for underwater surveys using a benthic sledge.
Sledge location (longitude and latitude) of the benthic sledge can be estimate from boat position with **DeepS_location()**. Twins green laser positions can be extract from movie using **DeepS_find_laser()** and correction of laser positions can be done with **DeepS_correct_laser()**. 


# Installation

To install *RDeepSledge* Package, use **devtools::install_github("FROBIN02/Rdeepsledge")**.

## Estimating Sledge location from boat position


*in process*


## Extraction of laser point locations

Note: the AV package must be installed separately.


```{r find laser,  eval = FALSE, echo = TRUE}

library(Rdeepsledge)

MP4_file <- file.choose ()

loclasers<- DeepS_find_laser(MP4_file,FALSE,120)

```

Here, *MP4_file* is your video file, *FALSE* is the parallelization option (not stable for this version), and the number *120* corresponds to the number of frames between each estimation.

**WARNING** This function may run for several hours,days. The conversion of the video into frames can take up space, but the temporary folder is deleted at the end of the execution.


## Example for correcting laser position files

```{r exemple laser, eval=FALSE,message=FALSE}

library(Rdeepsledge)

loclasers <- read.table("laser_position#yourvideo#.txt") # in "USER/document"

```

The file extracted from the video is stored under the name "RESULT" and a backup is made in USER/document in the form laser_position*namesofyourvideo*.txt.

For the example, the data MPO_REFURE_source.R replaces the data file.

```{r corr laser data,eval=TRUE,warning=FALSE,message=FALSE}
library(Rdeepsledge)

mylaser_coor <- DeepS_correct_laser(loclasers)

```

exemple de données


```{r cor res, echo=FALSE,eval=TRUE,message=FALSE,results='asis'}
library(knitr)
tabsyn <- head(mylaser_coor$DATA)
   tabsyn %>%
  kbl(caption = "Table 1:tableau de données avec balise") %>%
  kable_classic(full_width = T, html_font = "Cambria")
```

The details of the fields are not yet available for this version...

Next, a figure extracted from the corrected data. 

```{r corr laser graph,echo=FALSE, warning=FALSE, message=FALSE,fig.width=8, fig.height=8, results='asis'}

mylaser_coor$GRAPH

```


